% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{How can developers help in the process of making games more accessible to people with disabilities.}

% Please do not change the subtitle
\subtitle{COMP130 - Software Engineering}

% Please put your student number in the author field
\author{1706258}

\begin{document}

\maketitle

\abstract{In this essay i will go into how can developers help to make games more accessible to people who still want to play games but are not able to do so in the same way as a normal gamer, an example would be if someone only had one arm how could developers help in the process of making the game so that it is more accessible.}

\section{Introduction}
In this essay i will be going into depth on how developers can aid in the proccess of helping gamers with disabillitys play games just like everybody else can, Wether this be physical aid or non physical, i will go into the ways that developers can work around these constraints and give gamers with disabillites the same level of joy out of video games that all games have.
"A survey study has indicated that 63% of the population in the US plays video games and estimated 51% of gamers play games at least every week [3]. Despite these large numbers, disability gamers are a small portion of people whom playing games. Approximately, 11% of US population finds difficultly to play games as reason of disability."

This cite from [7] shows that 11% of people in the US population finds difficulties playing games from disabillity, with this figure in mind it shows that there is improvement to be made on the accessibility of the modern video game, in time this number will go lower thanks to the technology that is now available.
One way to begiin is to see how other developers have found way to help gamers with disabillitys in the past and how today technology can advance these previous methods.

\section{Your section title here}
Able Gamers
Able Gamers is an online forum for people with disabilities who are gamers, Able Gamers have a website in which they talk about how they have assisted technology for people with disabilities, you can apply through there website and also apply for funding for the technology.
Able Gamers has teamed up with Evil Controllers which we will touch on in accessible controllers later on in this essay.

Adaptive Controllers
There are adaptive Controllers for people who have physical disabilities these controllers are available for Xbox and PS4, these can be done through a service called ReMap which help to create controllers that are easier to use and more intuitive to the person.
Evil Controllers partnered with Able Gamers which was talked about earlier I this essay, Evil Controllers believe in the fact that everyone would be able to play games a receive the same amount of joy as everyone else, Evil Controllers take commissions which are available through Able Gamers or you can call them if you wish to talk to them independently.
There is a controller that transfers all important commands to three touch pads so that there is more accessibility for people with physical disabilities and also anyone with memory problems.
An avenue for accessibility is Virtual Reality in which people can be put into a different reality through computer rendering, there are plus sides to this and down sides, the plus sides are that some people will be able to see things that they never through possible and have a new experience, but on the other side there is a few problems with virtual reality such as it being having reliant on motion  technology it is a problem for people who can use the motion technology controllers.

Accessible Games
Games such as Overwatch have made there games accessible by having various options for button configurations to where you can play the game with a few button presses.
In today's games being able to remap the controls is a must have for any game, also having a easy to learn intuitive user interface, vision is also  a big factor to make sure you don't convey important messages through colour alone, hearing is also important such as adding subtitles for important information.
Other ways to make your game more accessible are support more than one input device just in case someone wants to use a specially modified controller for your game but if you do not support it then they will not get to play your game, add support for windowed mode for any kind of overlaying information such as Keyboards, it helps to reinforce any information that is text based with visuals and/or speech,if the game is 3D based and has a field of view add an option to change said field of view, another way is to keep background noise to a minimum so that anyone with hjearing difficulties can hear loand and clearly what is being said.

Colour Blindness
Take people with color blindness for example, older technology was not as equipped to deal with this as today's technology, when I look at the options in a modern day video game there is usually an option for people with colour blindness, but in older video games this was not the case.
There are three common types of color blindness
1. Protanopia - unable to percieve red light, makes red and greens look murky but maes blues and yellows stand out.

2. Deuteranopia - unable to percieve green light, makes red and greens look murky but maes blues and yellows stand out.

3. Tritanopia - unable to percieve blue light, makes greens look murky and reds appera pink.

ther has been many attempts at making vidoe games more accessible to people who suffer from colour blindness, Call Of Duty to start with only had colorblind options for the mini-map and HUD but now with newer technology Call of Duty has now made a full screen colorblind mode that recolours everything in the game, DOOM most recently had the same modes for each type of color blindness and made it easiley accssible through an in game menu, Ovberwatch is also a very peopular game that has these options also.
 In some cases the modern color blind options sometimes don't work for some people and this is still an current issue but is hopefully going to be solved by the advancement of technology.


\section{Conclusion}
in conclusion this essay has looked into how past technology can be updated to be more efficient at solving the said problem, i have also looked closely at organisations that offer support and grants to apply for said technology, and the type of technology they provide and how it can work better for some people, i have also gone down a new route of Virtual Reality in this paper i have discussed the pros and cons of the technology and how it can benefit people.

\bibliographystyle{ieeetran}
\bibliography{references}

(1)Analysis and review of apps and serious games on mobile devices intended for people with visual impairment - M.I. Torres-Carazo, M.J. Rodríguez-Fórtiz, M.V. Hurtado.

(2)Video gaming accessibility - Drew McPheron.

(3)Game Accessibility: Enabling Everyone to Play - Lee Garber.

(4)The production of learning objects with accessibility for people with disabilities from strategies of gamification and transmedia storytelling - Leonardo Enrico Schimmelpfeng, Vania Ribas Ulbricht, Luciane Fadel, Claudia Regina Batista, Graziela de Souza Sombrio.

(5)Video game Accessibility: A Legal Approach - George M. Powers

(6)Game Not Over Acessibillity issues in video games - Kevin J Bierre

(7) EEG headset supporting mobility impaired gamers with game accessibility - Omamah Hawsawi, Sudhanshu K. Semwal.

(8) A console interface for game accessibility to people with motor impairments - L.Fanucci,  F.Iacopetti,  R.Roncella.


\end{document}
